---
title: "When do shooting percentages become reliable?"
author: "Chris Gauthier"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load libraries
library(tidyverse)

# Load data
shots <- read_csv("NBA_2024_Shots.csv")

# Drop unnecessary columns
shots2 <- shots %>%
  select(-SEASON_1, -SEASON_2, -TEAM_ID, -PLAYER_ID, -GAME_ID, -HOME_TEAM, 
         -AWAY_TEAM, -EVENT_TYPE, -ZONE_NAME, -ZONE_ABB, -LOC_X, -LOC_Y)

# Format dates
shots3 <- shots2 %>%
  mutate(GAME_DATE = as.Date(shots2$GAME_DATE, format="%m-%d-%Y"))

# Number of shots
fg <- shots3 %>%
  group_by(PLAYER_NAME) %>% mutate(shot_num = row_number())

fg2 <- fg %>%
  group_by(shot_num) %>%
  summarize(attempts = n(), makes = sum(SHOT_MADE))

# Player shot count elbow chart
player_elbow <- ggplot(data=fg2, aes(x=shot_num, y=attempts)) +
  geom_point() +
  xlab("Number of Shots") +
  ylab("Number of Players")
```

## Introduction

In this document I will perform an analysis where I identify at what number of shot attempts do shooting percentages start to become reliable.

This will include an analysis of R-Squared values comparing the collective players' n-attempt samples with their season-long percentages.

I will analyze 

- FG%
- 2PFG%
- 3PFG%
- eFG%
- TS%

## Methodology

*Explination on random sampling of n-attempts as opposed to first n-attempts*

I chose the arbitrary value of 500 shot attempts as a cut off for the population of players I examined, which brought me to the 174 highest-volume shooters over the course of the 2023-2024 NBA season.

## Deciding on a qualifying # of shot attempts

```{r shooting-sample-reliability, echo=FALSE}
player_elbow
```

## Next steps

I performed this analysis with a timeline of 1.5-2 weeks and limited bandwidth. If I had more time, there are a number of ways I think I could have taken this analysis.

### Ranges/confidence intervals

*Explination*

### Experiment with other measures of accuracy/correlation

*Explination*

### Clean code practices

*Explination*